FoRTE baseline

### 2019-07-23 analysis/paper/paper.Rmd
Update within vs across uncertainty paragraph

Across all variables, parameter uncertainty (across ensembles within each model configuration) was at least as large, and usually larger, than structural uncertainty (Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question.
Facilitating horizontal competition by enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) reduced uncertainty in aboveground biomass, diversity, and primary productivity.
Using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased uncertainty in leaf area index, aboveground biomass, and diversity, but did not have a consistent effect on uncertainty in productivity.
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) had effectively no impact on simulation uncertainty (_but see caveat at the beginning of results_.)

>>>>

Except for the configurations with persistently low productivity, parameter uncertainty (across ensembles within each model configuration) was much larger than structural uncertainty (variance in ensemble means across configurations; Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question.
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) slightly reduced variability in primary productivity, slightly increased variability in Shannon diversity, and had mixed effects on aboveground biomass and total leaf area.
Enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) dramatically decreased variability in primary productivity and Shannon diversity and increased variability in leaf area, and had mixed effects on aboveground biomass.
reduced variance in aboveground biomass, diversity, and primary productivity.
Finally, using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased variance in leaf area index, aboveground biomass, and diversity, but did not have a consistent effect on variance in productivity productivity.
